00-OD-preparation

### 2022-04-06 data-raw/00-OD-preparation.Rmd
meeting with javier

First, we count the number of trips coming from each origin:
```{r}
Otrips_zona <- OD_v_Oc_Dt %>% group_by(VORIZT1259)  %>% summarise(Otrips = (n())) # we group by the origin ZT1259 ID and then we summarize the number of rows that have the same ZT using the summarize() function and the n() function to create a new 'Otrips' column.

head(Otrips_zona,12)
```

Now, we add this new column to the zonas sf object:
```{r}
zn <- zn %>% merge(Otrips_zona, by.x = "ZT1259", by.y="VORIZT1259")

@@

a simple plot:
```{r}
ggplot() +
  geom_sf(data = zn,
          aes(fill = Otrips),
          color  = NA) +
  scale_fill_distiller(palette = "Spectral")
```

>>>>

First, we count the number of trips coming from each origin:
```{r}
Dtrips_zona <- OD_v_Oc_Dt %>% group_by(VDESZT1259)  %>% summarise(Dtrips = (n())) # we group by the origin ZT1259 ID and then we summarize the number of rows that have the same ZT using the summarize() function and the n() function to create a new 'Otrips' column.

head(Dtrips_zona,12)
```

Now, we add this new column to the zonas sf object:
```{r}
zn <- zn %>% merge(Dtrips_zona, by.x = "ZT1259", by.y="VDESZT1259")

@@

a simple plot:
```{r}
ggplot() +
  geom_sf(data = zn,
          aes(fill = Dtrips),
          color  = NA) +
  scale_fill_distiller(palette = "Spectral")
```
